Download final data

### 2024-07-25 analysis/data-final.qmd
Add link to docker repo + rearrange stuff

---
title: "Download final data"
format:
  html:
    code-tools: false
---

<table class="table">
  <thead>
    <tr>
      <th scope="col">Program</th>
      <th scope="col">File</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <td>CSV file for any program</td>
      <td><a class="btn btn-primary" target="_blank" href="#">{{< fa table >}} &ensp;<span class="font-monospace">daily_panel.csv</span></a></td>
    </tr>
    <tr>
      <td><span class="font-monospace">.rds</span> file for R<br><span class="small">(load with `df <- readRDS("daily_panel.rds")`)</small></td>
      <td><a class="btn btn-primary" target="_blank" href="#">{{< fa brands r-project >}} &ensp;<span class="font-monospace">daily_panel.rds</span></a></td>
    </tr>
    <tr>
      <td><span class="font-monospace">.dta</span> file for Stata<br><span class="small">(load with `use "daily_panel.dta"`)</small></td>
      <td><a class="btn btn-primary" target="_blank" href="#">{{< fa table-cells >}} &ensp;<span class="font-monospace">daily_panel.dta</span></a></td>
    </tr>
  </tbody>
</table>

>>>>

---
title: "Download final data"
format:
  html:
    code-tools: false
    toc: false
---

```{r include=FALSE}
# Add these final data files as targets dependencies
library(targets)
tar_load(c(data_weekly_stata, data_weekly_csv, data_weekly_rds,
           data_quarterly_stata, data_quarterly_csv, data_quarterly_rds))
tar_load(c(data_weekly_stata_website, data_weekly_csv_website, data_weekly_rds_website,
           data_quarterly_stata_website, data_quarterly_csv_website, data_quarterly_rds_website))
```

The cleaned data is available in three formats:

- CSV file for any program
- `.rds` file for R <span class="small">(load with `df <- readRDS("weekly_panel.rds")`)</span>
- `.dta` file for Stata <span class="small">(load with `use "weekly_panel.dta"`)</span>

## Weekly data

<a class="btn btn-primary btn-sm" target="_blank" href="data/weekly_panel.csv">{{< fa table >}} &ensp;<span class="font-monospace">weekly_panel.csv</span></a> &emsp; <a class="btn btn-success btn-sm" target="_blank" href="data/weekly_panel.rds">{{< fa brands r-project >}} &ensp;<span class="font-monospace">weekly_panel.rds</span></a> &emsp; <a class="btn btn-warning btn-sm" target="_blank" href="data/weekly_panel.dta">{{< fa table-cells >}} &ensp;<span class="font-monospace">weekly_panel.dta</span></a>

## Quarterly data

<a class="btn btn-primary btn-sm" target="_blank" href="data/quarterly_panel.csv">{{< fa table >}} &ensp;<span class="font-monospace">quarterly_panel.csv</span></a> &emsp; <a class="btn btn-success btn-sm" target="_blank" href="data/quarterly_panel.rds">{{< fa brands r-project >}} &ensp;<span class="font-monospace">quarterly_panel.rds</span></a> &emsp; <a class="btn btn-warning btn-sm" target="_blank" href="data/quarterly_panel.dta">{{< fa table-cells >}} &ensp;<span class="font-monospace">quarterly_panel.dta</span></a>
